Widespread nitrous oxide undersaturation in U.S. lakes and reservoirs

### 2023-08-31 manuscript/manuscript_file.Rmd
Minor tweaks to manuscript files

-   incorporate in Methods section how/why size is incorporated as categorical variable and continuos variable.
-   Mike will take a stab at big SI table.
-   Citation "epa_data" isn't populating citation 11 in bibliography. The bibTex entry is classified as a "website". Roy, can you attempt to make this citation play nice with nature_geosciences.csl?
-   netCDF data from Lauerwald
-   Letters vs article format at Nature Geosciences
-   Add quantitative NO3 values to Fig.3B and Fig. 5B legend.
-   Add quantitative size category values to Fig. 5A legend.

@@

Total N~2~O flux from the surface of CONUS waterbodies is a function of N~2~O emission rates and waterbody surface areas. The four smallest size classes (\< 50 Ha) in the survey design contained `r round(proportionSmallNumber, 2) * 100`% of all lakes in the population, but contributed only `r round((FluxBySize %>% filter(size_cat != "50_max") %>% select(estimate) %>% summarise(tot_small = sum(estimate)) %>% pull())/(FluxBySize %>% filter(size_cat == "50_max") %>% select(estimate) %>% pull()) * 100, 0)`% to the N~2~O flux from CONUS waterbodies **[(Fig. 6C)]**. The reason for this pattern is two-fold. First, lakes in the smaller size classes constituted only `r round(proportionSmallSA, 2) * 100`% of total waterbody surface area, thereby limiting their N~2~O flux. Secondly, widespread N~2~O uptake in these size classes largely offset the very high emission rates predicted to occur in a minority of the population **[(Fig. 6A)].** Waterbodies in the largest size class (\> 50 Ha) contained only `r round(1 - proportionSmallNumber, 2) * 100`% of the total number of lakes in the population, but had `r round(1-proportionSmallSA, 2) * 100`% of total lake surface area. This lake size class had the greatest N~2~O flux (mean = `r FluxBySize %>% filter(size_cat == "50_max") %>% select(estimate) %>% pull() %>% round(0)` metric tons N~2~O year^{-1}), but the flux estimate is poorly constrained with a 95% credible interval of `r FluxBySize %>% filter(size_cat == "50_max") %>% select(LCL) %>% pull()` - `r FluxBySize %>% filter(size_cat == "50_max") %>% select(UCL) %>% pull()` metric tons N~2~O year^{-1} **[(Fig. 6C)]**. While uncertainty in N~2~O emission rates was smallest for large lakes **(Fig. 6A)**, these small uncertainties propagated to large uncertainties in flux when expressed across the surface area of large waterbodies.

@@

[a]note overlap between all ecoregion. all ecoregions overlap 0 Note relationship with lake size.

>>>>

-   incorporate in Methods section how/why size is incorporated as categorical variable and continuos variable.
-   Citation "epa_data" isn't populating citation 11 in bibliography. The bibTex entry is classified as a "website". Roy, can you attempt to make this citation play nice with nature_geosciences.csl?
-   Letters vs article format at Nature Geosciences
-   Add quantitative NO3 values to Fig.3B and Fig. 5B legend.
-   nitrate in methods
-   Lester Luan and Jana Compton for internal tech reviews.

@@

Total N~2~O flux from the surface of CONUS waterbodies is a function of N~2~O emission rates and waterbody surface areas. The four smallest size classes (\< 50 Ha) in the survey design contained `r round(proportionSmallNumber, 2) * 100`% of all lakes in the population, but contributed only `r round((FluxBySize %>% filter(size_cat != "50_max") %>% select(estimate) %>% summarise(tot_small = sum(estimate)) %>% pull())/(FluxBySize %>% filter(size_cat == "50_max") %>% select(estimate) %>% pull()) * 100, 0)`% to the N~2~O flux from CONUS waterbodies **[(Fig. 6C)]**. The reason for this pattern is two-fold. First, lakes in the smaller size classes constituted only `r round(proportionSmallSA, 2) * 100`% of total waterbody surface area, thereby limiting their N~2~O flux. Secondly, widespread N~2~O uptake in these size classes largely offset the very high emission rates predicted to occur in a minority of the population **[(Fig. 6A)].** Waterbodies in the largest size class (\> 50 Ha) contained only `r round(1 - proportionSmallNumber, 2) * 100`% of the total number of lakes in the population, but had `r round(1-proportionSmallSA, 2) * 100`% of total lake surface area. This lake size class had the greatest N~2~O flux (mean = `r FluxBySize %>% filter(size_cat == "50_max") %>% select(estimate) %>% pull() %>% round(0)` metric tons N~2~O year\^{-1}), but the flux estimate is poorly constrained with a 95% credible interval of `r FluxBySize %>% filter(size_cat == "50_max") %>% select(LCL) %>% pull()` - `r FluxBySize %>% filter(size_cat == "50_max") %>% select(UCL) %>% pull()` metric tons N~2~O year\^{-1} **[(Fig. 6C)]**. While uncertainty in N~2~O emission rates was smallest for large lakes **(Fig. 6A)**, these small uncertainties propagated to large uncertainties in flux when expressed across the surface area of large waterbodies.

@@
